---
title: "Interactive Box Plot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interactive Box Plot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  eval = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r}
library(boxly)
```

# Overview

Interactive box plots refers to the graphical representations that allow users to explore and 
analyze data through an interactive interface. They provide a way to visualize the distribution, 
central tendency, and variability of a dataset using a box-and-whisker plot, while also 
providing additional interactivity for deeper exploration.

Some common interactive features of the box plots include: 

 - Hovering: When the user hovers the mouse cursor over a specific part of the plot, additional information 
   related to that specific data point or summary statistic is displayed. This includes the descriptive 
   statistics (N, Mean, Median, Q1, Q3, Min and Max), Subject ID and Change from Baseline 
   
 - Filtering: It is possible to apply filters to the data, enabling users to select specific Parameter 
   from a domain (Labs, Vitals, ECG)
  
# Mental model

Creating the box plot using this package involves the below steps:

  - Create a metadata object using the metalite package
  - Call `prepare_boxly()` function to prepare the metadata as required by the user 
  - Call `boxly()` function to create the interactive plot


## Example 1: Interactive Box Plot Using Labs Data

Step 1: Create a metadata object using the metalite package

```{r}
analysis_plan <- metalite::plan(
  analysis = "boxly",
  population = "apat",
  observation = "wk12",
  parameter = "SODIUM;K;CL"
)

meta <- metalite::meta_adam(
  population = boxly_adsl,
  observation = boxly_adlb
) |>
  metalite::define_plan(analysis_plan) |>
  metalite::define_population(
    name = "apat",
    group = "TRTA",
    subset = SAFFL == "Y",
    label = "Safety Population"
  ) |>
  metalite::define_observation(
    name = "wk12",
    group = "TRTA",
    var = "PARAM",
    subset = AVISITN <= 12 & !is.na(CHG),
    label = "Weeks 0 to 12"
  ) |>
  metalite::define_parameter(
    name = "SODIUM",
    label = "Sodium (mmol/L)",
    subset = PARAMCD == "SODIUM"
  ) |>
  metalite::define_parameter(
    name = "K",
    label = "Potassium (mmol/L)",
    subset = PARAMCD == "K"
  ) |>
  metalite::define_parameter(
    name = "CL",
    label = "Chloride (mmol/L)",
    subset = PARAMCD == "CL"
  ) |>
  metalite::define_analysis(
    name = "boxly",
    label = "Interactive Box Plot",
    x = "AVISITN",
    y = "CHG"
  ) |>
  metalite::meta_build()
```

Step2: Call `prepare_boxly()` function to prepare the metadata as required by the user

```{r}
outdata <- prepare_boxly(meta)
outdata
```

Step 3: Call `boxly()` function to create the interactive plot

```{r}
boxly(outdata)
```

## Example 2: Interactive Box Plot Using Vital Signs Data

```{r}
analysis_plan <- metalite::plan(
  analysis = "boxly",
  population = "apat",
  observation = "wk12",
  parameter = "DIABP;PULSE;SYSBP"
)

meta <- metalite::meta_adam(
  population = boxly_adsl,
  observation = boxly_advs
) |>
  metalite::define_plan(analysis_plan) |>
  metalite::define_population(
    name = "apat",
    group = "TRTA",
    subset = SAFFL == "Y",
    label = "Safety Population"
  ) |>
  metalite::define_observation(
    name = "wk12",
    group = "TRTA",
    var = "PARAM",
    subset = AVISITN <= 12 & !is.na(CHG),
    label = "Weeks 0 to 12"
  ) |>
  metalite::define_parameter(
    name = "DIABP",
    label = "Diastolic Blood Pressure (mmHg)",
    subset = PARAMCD == "DIABP"
  ) |>
  metalite::define_parameter(
    name = "PULSE",
    label = "Pulse Rate (BEATS/MIN)",
    subset = PARAMCD == "PULSE"
  ) |>
  metalite::define_parameter(
    name = "SYSBP",
    label = "Systolic Blood Pressure (mmHg)",
    subset = PARAMCD == "SYSBP"
  ) |>
  metalite::define_analysis(
    name = "boxly",
    label = "Interactive Box Plot",
    x = "AVISITN",
    y = "CHG"
  ) |>
  metalite::meta_build()

meta |>
  prepare_boxly() |>
  boxly()
```

## Example 3: Interactive Box Plot Using ECG Data

```{r}
analysis_plan <- metalite::plan(
  analysis = "boxly",
  population = "apat",
  observation = "wk12",
  parameter = "ARATE;PR;QRS"
)

meta <- metalite::meta_adam(
  population = boxly_adsl,
  observation = boxly_adeg
) |>
  metalite::define_plan(analysis_plan) |>
  metalite::define_population(
    name = "apat",
    group = "TRTA",
    subset = SAFFL == "Y",
    label = "Safety Population"
  ) |>
  metalite::define_observation(
    name = "wk12",
    group = "TRTA",
    var = "PARAM",
    subset = AVISITN <= 12 & !is.na(CHG),
    label = "Weeks 0 to 12"
  ) |>
  metalite::define_parameter(
    name = "ARATE",
    label = "Atrial Rate (beats/min)",
    subset = PARAMCD == "ARATE"
  ) |>
  metalite::define_parameter(
    name = "PR",
    label = "PR Interval (msec)",
    subset = PARAMCD == "PR"
  ) |>
  metalite::define_parameter(
    name = "QRS",
    label = "QRS Interval (msec)",
    subset = PARAMCD == "QRS"
  ) |>
  metalite::define_analysis(
    name = "boxly",
    label = "Interactive Box Plot",
    x = "AVISITN",
    y = "CHG"
  ) |>
  metalite::meta_build()

meta |>
  prepare_boxly() |>
  boxly()
```
