---
title: "Boxly Hover Label"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Boxly Hover Label}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  eval = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

> This document will guide the developers on how to customize the hover label based on the study needs.


# Overview

Hovering is one of the interactive feature for the box plots. When the user hovers the mouse cursor over a specific part of the plot, additional information related to that specific data point or summary statistic is displayed. 


Hovering feature in interactive box plots contains two parts:**Hover label of box** and **Hover label of outlier**.

- Hover label of box is to display the descriptive statistics for the plots on the hovering box.

  For example: N, Mean, Median, Q1, Q3, Min and Max

- Hover label of outlier is to display the information for the outlier out of box.

  For example: Subject ID, Change from Baseline and etc.
  
  
# Hover label in function `prepare_boxly()`:

**hover_var_outlier**: A character vector of hover variables for outlier.

```
prepare_boxly(
  meta,
  hover_var_outlier = c("USUBJID", metalite::collect_adam_mapping(meta, analysis)$y)
  ...
)
```

Here, the information for the outlier out of the box could be defined as hover_var_outlier. The developers could update hover_var_outlier to cutomize what to display in the hovering.


# Hover label in function `boxly()`:

**hover_summary_var**: A character vector of statistics to be displayed on hover label of box.

**hover_outlier_label**: A character vector of hover label for outlier.
```
boxly <- function(outdata,
                  hover_summary_var = c("n", "min", "q1", "median", "mean", "q3", "max"),
                  hover_outlier_label = c("Participant ID", "Parameter value"),
                  ...)
```

The preferred display label name in hover label of outlier corresponding to the value from meta objects could be defined as hover_outlier_label. The default label are "Participant ID" showing the "USUBJID" and the "Parameter value" showing the "CHG" (Change from Baseline). The developer could add more information (i.e. Baseline value, Analysis date). Make sure that the number of hover_outlier_label should match hover_var_outlier.

The descriptive statistics displayed on hover label of box are defined as hover_summary_var. The developer could choose to display only partial descriptive statistics among 
"n", "min", "q1", "median", "mean", "q3" or "max". The default value are including all these descriptive statistics.


# Example 1: Add Hover Label of outlier

In this example, we plan to add more hover labels for outliers.

```{r}
library(boxly)
```

Step1: Create a list of metadata using [meta_boxly()](https://merck.github.io/boxly/reference/meta_boxly.html). Using Lab data as example.

```{r}
meta <- meta_boxly(
  boxly_adsl,
  boxly_adlb,
  population_term = "apat",
  observation_term = "wk12",
  observation_subset = AVISITN <= 12 & !is.na(CHG)
)
```

Step2: Call [prepare_boxly()](https://merck.github.io/boxly/reference/prepare_boxly.html) function to prepare the metadata as required by the user. In this example, we plan to add Baseline Value and Analysis Date, so besides the default "USUBJID" and "CHG"(as y axis label collected from meta mapping object),"BASE" and "ADT" are also included in the hover_var_outlier.

```{r}
outdata <- prepare_boxly(meta,
                         hover_var_outlier = c("USUBJID", metalite::collect_adam_mapping(meta, meta$plan$analysis)$y,"BASE","ADT"))
```

Step 3: Call [boxly()](https://merck.github.io/boxly/reference/boxly.html) function to create the interactive plot. In this step, "Base Value" and "Analysis Date" are included in hover_outlier_label as displaying label for "BASE" and "ADT" which were defined in hover_var_outlier from previous step.

```{r}
boxly(outdata,
      hover_outlier_label = c("Participant ID", "Parameter value","Base Value","Analysis Date"))
```
Here, you will notice "Participant ID", "Parameter value","Base Value"and "Analysis Date" are all displaying when pointing to the outlier plot. 

# Example 2: Choose Hover Label of box

In this example, we plan to only display number of participant, Q1, mean, median, Q3 for the hover label of box.

Step1: Create a list of metadata using [meta_boxly()](https://merck.github.io/boxly/reference/meta_boxly.html). Using Vital Sign data as example.

```{r}
meta_boxly(
  boxly_adsl,
  boxly_advs,
  population_term = "apat",
  observation_term = "wk12",
  observation_subset = AVISITN <= 12 & !is.na(CHG)
)
```

Step2: Call [prepare_boxly()](https://merck.github.io/boxly/reference/prepare_boxly.html) function to prepare the metadata as required by the user. In this step, we did not change hover_var_outlier, so the hover label for the outlier will display the default value "Participant ID" and "Parameter value" for "USUBJID" and "CHG".

```{r}
outdata <- prepare_boxly(meta)
```

Step 3: Call [boxly()](https://merck.github.io/boxly/reference/boxly.html) function to create the interactive plot. We only include "n" for number of participant, "q1" for Q1, "median" for Median, "mean" for Mean, "q3" for Q3. We remove the "min" and "max" from the default value.

```{r}
boxly(outdata,
      hover_summary_var = c("n", "q1", "median", "mean", "q3"))
```
Here, you will notice that only number of participant, Q1, mean, median, Q3 are displaying when pointing to the plot in the box.

# Example 3: Cutomize Label of outlier and Hover Label of box
In this example, we plan to combine Example 1 and Example 2 to customize label of outlier and label of box at the same step. Using ECG data as example.

```{r}
meta_boxly(
  boxly_adsl,
  boxly_adeg,
  population_term = "apat",
  observation_term = "wk12",
  observation_subset = AVISITN <= 12 & !is.na(CHG)
)
```

```{r}
outdata <- prepare_boxly(meta,
                         hover_var_outlier = c("USUBJID", metalite::collect_adam_mapping(meta, meta$plan$analysis)$y,"BASE","ADT","AVAL"))
```

```{r}
boxly(outdata,
      hover_summary_var = c("n", "q1", "median", "mean", "q3"),
      hover_outlier_label = c("Participant ID", "Parameter value","Base Value","Analysis Date","Analysis Value"))
```

Here, you will notice that both label of outlier and label of box are different from the default value. Please follow above steps to customize the interactive box plot hover label to meet your study needs. 
